Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-09 jss/article.tex
[skip ci] update examples.

%> as.character(res$module)
%[1] "Apoptosis:HEDGEHOG"          "Apoptosis:AKT_MTOR"
%[3] "DNA_repair"                  "DNA_repair:G1_CC_PHASE"
%[5] "ACSN_master:AKT_MTOR"        "ACSN_master:G1_CC_PHASE"
%[7] "Survival:S_PHASE_CHECKPOINT"

\begin{table}[h!]
  \centering
  \caption{ACSN maps enrichment for genes differentially expressed between ER
positive and ER negative samples in breast cancer.  Module : name of the
module. Mod. size: size of the module. Nb genes: number of genes from input
which are found in the module. pval: corrected p-value.}
\label{tab:table_mainz}

\begin{tabular}{l|c|c|c}
\hline
Module & Mod. size & Nb genes & pval \\
\hline
Apoptosis:HEDGEHOG &  &  & 1.04e-08 \\
Apoptosis:AKT\_MTOR &  &  & 1.04e-08 \\
DNA\_repair &  &  & 1.04e-08 \\
DNA\_repair:G1\_CC\_PHASE &  &  & 1.04e-08 \\
ACSN\_master:AKT\_MTOR &  &  & 1.04e-08 \\
ACSN\_master:G1\_CC\_PHASE &  &  & 1.04e-08 \\
Survival:S\_PHASE\_CHECKPOINT &  &  & 1.04e-08 \\
\hline

>>>>

dim(results)
[1] 7 9
\end{verbatim}

\begin{table}[h!]
  \centering
  \caption{ACSN maps enrichment for genes differentially expressed between ER
positive and ER negative samples in breast cancer.  Module : name of the
module. Mod. size: size of the module. Nb genes: number of genes from input
which are found in the module. pval: raw p-value. Cor. pval: corrected p-value.}
\label{tab:table_mainz}

\begin{tabular}{l|c|c|c|c}
\hline
Module & Mod. size & Nb genes & pval & Cor. pval\\
\hline
Apoptosis:HEDGEHOG & 31 & 21 & 0.0016 & 0.042 \\
Apoptosis:AKT\_MTOR &  79 & 47 & 0.00037 & 0.038 \\
DNA\_repair & 335 & 163 & 0.0012 & 0.038 \\
DNA\_repair:G1\_CC\_PHASE &  25 & 18 & 0.0011 & 0.038 \\
ACSN\_master:AKT\_MTOR & 92 & 53 & 0.0005 & 0.038 \\
ACSN\_master:G1\_CC\_PHASE & 25 & 18 & 0.0011 & 0.038 \\
Survival:S\_PHASE\_CHECKPOINT & 8 & 8 & 0.0006 & 0.038 \\
\hline
